---
title: "R Notebook"
output: pdf_document
---

# Try to use title

```{r message = FALSE}
source('source.R')

path_panel <- read.csv('data/Output/adult_panel.csv') 

path_panel %>%  names %>%  as.data.frame


```


```{r}
path_panel %>%  filter(adult_cont_w2==1,  adult_cont_w3== 1 ) %>%  count
  
```

```{r}
#
path_panel %>%  filter(wave_1==1, wave_2==1, wave_3==1) %>%  count
```

## Wave 1

```{r wave_1_new}
path_panel %>% 
    filter(wave_1 == 1, wave_2 == 1, wave_3 ==1 ) %>% 
    count(smoking_status_full_w1)
```


```{r wave_1_check}

path_panel %>%  
    filter(adult_cont_w2==1, 
           adult_cont_w3== 1, 
           !is.na(R01R_A_CUR_ESTD_CIGS), 
           !is.na(R01R_A_CUR_EXPR_CIGS),
           !is.na(R01R_A_FMR_ESTD_CIGS),  
           !is.na(R01R_A_FMR_EXPR_CIGS )) %>% 
    count(R01R_A_CUR_ESTD_CIGS, R01R_A_CUR_EXPR_CIGS, R01R_A_FMR_ESTD_CIGS,  R01R_A_FMR_EXPR_CIGS )

```

## Wave 2

```{r wave_2_new}
path_panel %>% 
    filter(wave_1 == 1, wave_2 == 1, wave_3 ==1 ) %>% 
    count(smoking_status_full_w2)
```


```{r wave_2_check}

path_panel %>%  
    filter(adult_cont_w2==1, 
           adult_cont_w3== 1, 
           !is.na(R02R_A_CUR_ESTD_CIGS), 
           !is.na(R02R_A_CUR_EXPR_CIGS),
           !is.na(R02R_A_FMR_ESTD_CIGS_REV),  
           !is.na(R02R_A_FMR_EXPR_CIGS_REV)) %>% 
    count(R02R_A_CUR_ESTD_CIGS, R02R_A_CUR_EXPR_CIGS, R02R_A_FMR_ESTD_CIGS_REV,  R02R_A_FMR_EXPR_CIGS_REV)

```

# Wave 3
```{r wave_3_new}
path_panel %>% 
    filter(wave_1 == 1, wave_2 == 1, wave_3 ==1 ) %>% 
    count(smoking_status_full_w3)
```

```{r wave_3_check}

path_panel %>%  
    filter(adult_cont_w2==1, 
           adult_cont_w3== 1, 
           !is.na(R03R_A_CUR_ESTD_CIGS), 
           !is.na(R03R_A_CUR_EXPR_CIGS),
           !is.na(R03R_A_FMR_ESTD_CIGS_REV),  
           !is.na(R03R_A_FMR_EXPR_CIGS_REV)) %>% 
    count(R03R_A_CUR_ESTD_CIGS, R03R_A_CUR_EXPR_CIGS, R03R_A_FMR_ESTD_CIGS_REV,  R03R_A_FMR_EXPR_CIGS_REV)

```


## All Waves
```{r check_all_waves}
path_panel %>% 
    filter(wave_1 == 1, wave_2 == 1, wave_3 ==1 ) %>% 
    count(smoking_status_full_w1, smoking_status_full_w2, smoking_status_full_w3)
```

# Missings
-9 = Missing 
-8 = Don't know 5 0.0 %
-7 = Refused 10 0.0 %
-1 = Inapplicable


## Wave 1: Missing Data Analysis 

** 99 missings **
```{r}
path_panel %>%  filter(wave_1 == 1, wave_2 == 1, wave_3 == 1, is.na(smoking_status_full_w1)) %>% count(smoking_status_full_w1)
```
** 11: note 9 & 100 seem like mistakes ** 
```{r wave1_NA_cig_use_ever}

path_panel %>%  
  filter(wave_1 == 1, wave_2 == 1, wave_3 == 1,
         is.na(smoking_status_full_w1),
         cig_use_ever_w1 > 2) %>%
  count(cig_use_ever_w1, cig_current_freq_w1, cig_use_past30D_w1)

```
** 12 did not respond to current frequency question **
```{r}

path_panel %>%  
  filter(wave_1 == 1, wave_2 == 1, wave_3 == 1,
         is.na(smoking_status_full_w1), 
         cig_use_ever_w1 == 1,
         cig_current_freq_w1 < -1) %>% 
  count(cig_current_freq_w1)


```

** Remaining 76 did not answer question about liftime cigarette usage
```{r}

path_panel %>%  
  filter(wave_1 == 1, wave_2 == 1, wave_3 == 1,
         is.na(smoking_status_full_w1), 
         cig_current_freq_w1 >= 1) %>% 
  count(cig_current_freq_w1, cig_num_life_w1)

#19 + 10 + 5 + 5 + 24 +13 = 76
```


## Wave 2: Missing Data Analysis 

```{r}
path_panel %>% 
    filter(wave_1 == 1, wave_2 == 1, wave_3 ==1 ,is.na(smoking_status_full_w2)) %>% 
    count(cig_use_now_w2,cig_current_freq_w2  , cig_use_ever_w2, cig_num_life_w2)
  
```


**7 non-response to cig use ever**
```{r wave2_NA_cig_use_ever}
path_panel %>%  
  filter(wave_1 == 1, wave_2 == 1, wave_3 == 1,
         is.na(smoking_status_full_w2), is.na(cig_use_ever_w2)) %>% 
  count(cig_use_ever_w2)
```
**4 non-response to smoke past 30 days**
```{r}

path_panel %>% 
    filter(wave_1==1, wave_2==1, wave_3==1, !is.na(cig_use_ever_w2), is.na(smoking_status_full_w2)) %>% 
    count(cig_use_past30D_w2)
```

** 3 did not responde to cig use past 12 months question **
**709 did not get asked current frequency because they did not smoke in past 30 days or past 12 months**
```{r}
path_panel %>%  
  filter(wave_1 == 1, wave_2 == 1, wave_3 == 1,
         is.na(smoking_status_full_w2), !is.na(cig_use_ever_w2), cig_use_past30D_w2 != 1) %>% 
  count(cig_use_ever_w2, cig_use_past30D_w2, cig_use_past12M_w2 ,cig_current_freq_w2)
```


**3 non-response to current frequency**
```{r wave2_NA_cig_use_ever}
path_panel %>%  
  filter(wave_1 == 1, wave_2 == 1, wave_3 == 1,
         is.na(smoking_status_full_w2), !is.na(cig_use_ever_w2), cig_current_freq_w2 < -1) %>% 
  count(cig_use_past30D_w2, cig_current_freq_w2, cig_use_now_w2)
```
**Can't account for 351 students missing data on cig_num_life_w2**
```{r}
path_panel %>% 
  filter(wave_1 == 1, wave_2 == 1, wave_3 ==1,
         cig_use_ever_w2 == 1, 
         cig_current_freq_w2 == -1, 
         cig_use_past30D_w2==2, 
         cig_use_past12M_w2==2,
         is.na(smoking_status_w2)) %>% 
  count(cig_num_life_w2)


# 233 + 87 + 38 = 358
```


```{r}
path_panel %>% 
  filter(wave_1 == 1, wave_2 == 1, wave_3 ==1,
         cig_use_ever_w2 == 1, 
         cig_current_freq_w2 == -1, 
         cig_use_past30D_w2==2, 
         cig_use_past12M_w2==2,
         cig_num_life_w2 == -1,
         is.na(smoking_status_w2)) %>% 
  count(adult_cont_w2,cig_use_ever_w1, cig_use_ever_w2, cig_num_life_w1, cig_num_life_w2)

```




## Wave 3: Missing Data Analysis 

```{r}
 
path_panel %>% 
    filter(wave_1 == 1, wave_2 == 1, wave_3 ==1 ,is.na(smoking_status_full_w3)) %>% 
    count( cig_use_ever_w3, smoked_past12M_w3, cig_use_now_w3, cig_num_life_w3)
```

```{r}

path_panel %>% 
    filter(wave_1 == 1, wave_2 == 1, wave_3 ==1 ,is.na(smoking_status_full_w3)) %>% 
    count(cig_use_now_w3, cig_use_ever_w3, cig_num_life_w3)
```
